Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-09 draft.tex
add a couple of rows to draft
yesterday last work

\section{Parameter estimation}
Having two different datasets, we need to fit two separate models that represents those stations. During this estimation, our aim is to obtain a model that generalises our training dataset in such a way that forecasting becomes effective, also assessing errors analytically.
Obtaining such a reliable model will be the first step to verify any significant difference forecasting over the lockdown period.

@@

@@

@@

\section{Conclusion}
\subsection{Lockdown influence}
Even if the two models have the same order, they cannot be directly compared using the Information Criteria, for the Membach model works after a transformation pass, and they are fitted from different data.

We can still compare how the seasonalities differ with respect with each original dataset and between each other. We extract the seasonalities for each station highlighting the standard deviation confidence band for an estimated error of 67\%. This interval estimation lies on the assumption that values for each single hour in the hourly/weekly seasonality is Normally distributed, a slightly different assumption that is not necessarily refuted by the already seen Q-Q plots.

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.uccs_files/figure-latex/seasonalities/before-after-compare-1"}
		\caption{Uccle station}
		\label{fig:season.lockdown:uccs}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.mems_files/figure-latex/seasonalities/before-after-compare-1"}
		\caption{Membach station}
		\label{fig:season.lockdown:mems}
	\end{subfigure}
	\begin{center}
		\caption{Seasonalities computed before and after the lockdown}{\small Seasonalities are extracted together}
		\label{fig:season.lockdown}
	\end{center}
\end{figure}

As we can see in \figurename~\ref{fig:season.lockdown}, even if the seasonalities shapes seem very different, in particular regarding the weekly seasonality, the differences are still included in the highlighted confidence bands, apart from a few hours. This is true for both stations.
Yet, it is useful to notice that the weekly seasonalities include a possibly interesting daily component, influenced by the weekend drops in values.

%\subsection{Lockdown forecast divergence}
%Uccle: remodel on 52+18 (until 1st March 2020), forecast 2 months (8 weeks) => diff in MAPE
%Membach: remodel on 52+18 (until 1st March 2020), forecast 2 months (8 weeks) => diff in MAPE

\subsection{Limitations and future works}
The main problems of this projects that we identified are multiple seasonalities and the Normality assumption.

>>>>

\section{Methodology}
Having two different datasets, we need to fit two separate models that represents those stations. During this estimation, our aim is to obtain a model that generalises our training dataset in such a way that forecasting becomes effective, also assessing errors analytically.
Obtaining such a reliable model will be the first step to verify any significant difference forecasting over the lockdown period.

@@

Also, ARIMA parameters roots have values within the unit circle for the first two models, while for $\mathrm{ARIMA}(4,1,2)(0,1,1)_{168}$ two of the roots fall outside the unit circle, with values of $\approx1.49$ and $\approx1.80$.

@@

Parameters roots for both models have values within the unit circle.

@@

\subsection{Lockdown influence}
Even if the two models have the same order, they cannot be directly compared using the Information Criteria, for the Membach model works after a transformation pass, and they are fitted from different data.

\subsubsection{Seasonalities divergence}
We can still compare how the seasonalities differ with respect with each original dataset and between each other, by extracting the seasonalities for each station from before and after the lockdown (March, $14^{th}$).

We will highlight the confidence bands for an estimated error of 67\%. This interval estimation lies on the assumption that values for each single hour in the hourly/weekly seasonality is Normally distributed, a slightly different assumption that is not necessarily refuted by the already seen Q-Q plots.

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.uccs_files/figure-latex/seasonalities/before-after-compare-1"}
		\caption{Uccle station}
		\label{fig:season.lockdown:uccs}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.mems_files/figure-latex/seasonalities/before-after-compare-1"}
		\caption{Membach station}
		\label{fig:season.lockdown:mems}
	\end{subfigure}
	\begin{center}
		\caption{Seasonalities computed before and after the lockdown}{\small Seasonalities extracted together, confidence bands $\pm\mathrm{sd}$}
		\label{fig:season.lockdown}
	\end{center}
\end{figure}

As we can see in \figurename~\ref{fig:season.lockdown}, the seasonalities shapes seem different, in particular comparing the weekly seasonality. The seasonalities from before and after the lockdown are still included in the highlighted confidence bands, apart from a few hours. This is true for both stations.

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.mems_files/figure-latex/seasonalities/seasonplot-mean-sd-1"}
		\caption{Before lockdown}
		\label{fig:season.lockdown:msb:mems}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.mems_files/figure-latex/seasonalities/seasonplot-mean-sd-2"}
		\caption{After lockdown}
		\label{fig:season.lockdown:msa:mems}
	\end{subfigure}
	\begin{center}
		\caption{Seasonal plots for Membach station}
		\label{fig:season.lockdown:ms:mems}
	\end{center}
\end{figure}

The differences in shape are more highlighted checking the seasonal plots \cite{hyndman2018forecasting} in \figurename~\ref{fig:season.lockdown:ms:mems}. It is possible to notice a couple of changes: the Monday to Friday shapes are heavily flattened almost on the weekend values, and all the values are flattened towards 0. Both flattenings can be noticed checking the Uccle station, not showed for brevity.

\subsubsection{Forecast divergence}
\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.uccs_files/figure-latex/final-model-7"}
		\caption{Uccle station}
		\label{fig:forecast.lockdown:uccs}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{"project.mems_files/figure-latex/final-model-7"}
		\caption{Membach station}
		\label{fig:forecast.lockdown:mems}
	\end{subfigure}
	\begin{center}
		\caption{Forecasts from March, $2^{nd}$.}{\small In red the actual values, in black the forecasts. March, $14^{th}$ at midnight is highlighted.}
		\label{fig:forecast.lockdown}
	\end{center}
\end{figure}

By fitting the model\footnote{Data is different, because we are fitting the model on the original train+test dataset, but if we follow similar steps for both stations we can see that the final model we shall choose is the same. Also, the $\lambda$ parameter for the Box-Cox transformation of Membach data is estimated equally.} on data until March, $1^{st}$ we can compute forecasts for 8 weeks ahead, until April, $26^{th}$. As we can see in \figurename~\ref{fig:forecast.lockdown}, both stations overestimate starting after the lockdown. Uccle data in particular show a greater overestimation that can be noticed also by looking at the difference between the forecasted and measured values.

Analytically, the MAPE for Uccle doubles with respect to the previous test set ($\approx34\%$), and only 58\% and 78\% of the test data falls inside the confidence intevals (80\% and 95\%). Analysing the Membach station, we find those measures have comparable values to the previous test set: the MAPE remains at $16.6\%$, while 74\% and 90\% of data falls inside the confidence intervals.

%MEMS
%Test set inside the CI
%80% CI 	  74.18 %
%95% CI 	  89.58 %
%Errors:  forecast with ARIMA(2,0,0)(0,1,1)[168] 
%MSE= 117.9258   MAE= 7.709243   MAPE= 16.60103   RMSE= 10.85937   R2= 0.4777765

%UCCS
%Test set inside the CI
%80% CI 	  57.51 %
%95% CI 	  78.42 %
%Errors:  forecast with ARIMA(2,0,0)(0,1,1)[168] 
%MSE= 670897.8   MAE= 664.5903   MAPE= 33.94793   RMSE= 819.0835   R2= 0.5188538

%Uccle: remodel on 52+18 (until 1st March 2020), forecast 2 months (8 weeks) => diff in MAPE
%Membach: remodel on 52+18 (until 1st March 2020), forecast 2 months (8 weeks) => diff in MAPE

\section{Conclusions}
\subsubsection{Lockdown influence}
\subsection{Limitations and future works}
The main problems of this projects that we identified are multiple seasonalities and the Normality assumption.

### 2020-06-09 project.after.Rmd
yesterday last work

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)"))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

plots <- show_overlap_and_diff(
  final.testing, plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test set",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

@@

```{r seasonalities/before}
aggregated.before.lockdown <- seasonality.aggregate(before.lockdown)
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown-season.before.lockdown.168$seasonal, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
# this third iteration isn't actually needed
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown-season.before.lockdown.168$seasonal, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
seasonbase.before.lockdown.24 <- trend_season(aggregated.before.lockdown, 24)
seasonbase.before.lockdown.168 <- trend_season(aggregated.before.lockdown, 168)

plot_grid(
  autoplot(ts(seasonbase.before.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.before.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.before.lockdown.168$figure + rep(season.before.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.before.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.before.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.before.lockdown.168$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

```{r seasonalities/lockdown}
aggregated.after.lockdown <- seasonality.aggregate(after.lockdown)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown-season.after.lockdown.168$seasonal, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown-season.after.lockdown.168$seasonal, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
seasonbase.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
seasonbase.after.lockdown.168 <- trend_season(aggregated.after.lockdown, 168)

plot_grid(
  autoplot(ts(seasonbase.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.after.lockdown.168$figure[c(49:168,1:48)], frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.168$figure[c(49:168,1:48)] + rep(season.after.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.after.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.after.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.after.lockdown.168$figure[c(49:168,1:48)], col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

plot_grid(
  autoplot(ts(season.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.24$figure - season.after.lockdown.24$sd, ymax = season.after.lockdown.24$figure + season.after.lockdown.24$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Daily lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.24$figure - season.before.lockdown.24$sd, ymax = season.before.lockdown.24$figure + season.before.lockdown.24$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Daily before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Daily lockdown", "Daily before")),
  autoplot(ts(season.after.lockdown.168$figure[c(49:168,1:48)], frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = (season.after.lockdown.168$figure - season.after.lockdown.168$sd)[c(49:168,1:48)], ymax = (season.after.lockdown.168$figure + season.after.lockdown.168$sd)[c(49:168,1:48)]), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Weekly lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.168$figure - season.before.lockdown.168$sd, ymax = season.before.lockdown.168$figure + season.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.168$figure, col="Weekly before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before")),
nrow = 2)

autoplot(ts(seasonbase.after.lockdown.168$figure[c(49:168,1:48)], frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = (seasonbase.after.lockdown.168$figure - seasonbase.after.lockdown.168$sd)[c(49:168,1:48)], ymax = (seasonbase.after.lockdown.168$figure + seasonbase.after.lockdown.168$sd)[c(49:168,1:48)]), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="Weekly lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168$figure - seasonbase.before.lockdown.168$sd, ymax = seasonbase.before.lockdown.168$figure + seasonbase.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168$figure, col="Weekly before")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before"))
```
```{r seasonalities/seasonplot-mean-sd}
weekdays <- c("Monday", "Tuesday", "Wednseday", "Thursday", "Friday", "Saturday", "Sunday")

seasonbase.before.lockdown.168.df <- data.frame(hour=rep(1:24, 7), mean=seasonbase.before.lockdown.168$figure[1:168], sd=seasonbase.before.lockdown.168$sd[1:168], Weekday=rep(weekdays, each=24))
ggplot(data=seasonbase.before.lockdown.168.df) +
  geom_line(aes(hour, mean - sd, col=Weekday), alpha=.1) +
  geom_line(aes(hour, mean + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(hour, ymin = mean - sd, ymax = mean + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(hour, mean, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))

seasonbase.after.lockdown.168.df <- data.frame(hour=rep(1:24, 7), mean=seasonbase.after.lockdown.168$figure[c(49:168,1:48)], sd=seasonbase.after.lockdown.168$sd[c(49:168,1:48)], Weekday=rep(weekdays, each=24))
ggplot(data=seasonbase.after.lockdown.168.df) +
  geom_line(aes(hour, mean - sd, col=Weekday), alpha=.1) +
  geom_line(aes(hour, mean + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(hour, ymin = mean - sd, ymax = mean + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(hour, mean, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))
```

>>>>

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)") + xlab("Weeks") + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

plots <- show_overlap_and_diff(
  final.testing, plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test set",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2),
                plots[[2]] + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2),
                nrow = 2
                ))

@@

weekdays <- c("Monday", "Tuesday", "Wednseday", "Thursday", "Friday", "Saturday", "Sunday")
```

```{r seasonalities/before}
aggregated.before.lockdown <- seasonality.aggregate(before.lockdown)
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown-season.before.lockdown.168$seasonal, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
# this third iteration isn't actually needed
season.before.lockdown.24 <- trend_season(aggregated.before.lockdown-season.before.lockdown.168$seasonal, 24)
season.before.lockdown.168 <- trend_season(aggregated.before.lockdown-season.before.lockdown.24$seasonal, 168)
season.before.lockdown.168.df <- data.frame(Hour=rep(1:24, 7), figure=season.before.lockdown.168$figure[1:168], sd=season.before.lockdown.168$sd[1:168], Weekday=rep(weekdays, each=24))
seasonbase.before.lockdown.24 <- trend_season(aggregated.before.lockdown, 24)
seasonbase.before.lockdown.24.df <- data.frame(Hour=1:24, figure=seasonbase.before.lockdown.24$figure, sd=seasonbase.before.lockdown.24$sd)
seasonbase.before.lockdown.168 <- trend_season(aggregated.before.lockdown, 168)
seasonbase.before.lockdown.168.df <- data.frame(Hour=rep(1:24, 7), figure=seasonbase.before.lockdown.168$figure[1:168], sd=seasonbase.before.lockdown.168$sd[1:168], Weekday=rep(weekdays, each=24))

plot_grid(
  autoplot(ts(seasonbase.before.lockdown.24.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.before.lockdown.24.df$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.before.lockdown.168.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.before.lockdown.168.df$figure + rep(season.before.lockdown.24.df$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.before.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.before.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.before.lockdown.168.df$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

```{r seasonalities/lockdown}
aggregated.after.lockdown <- seasonality.aggregate(after.lockdown)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown-season.after.lockdown.168$seasonal, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.24 <- trend_season(aggregated.after.lockdown-season.after.lockdown.168$seasonal, 24)
season.after.lockdown.168 <- trend_season(aggregated.after.lockdown-season.after.lockdown.24$seasonal, 168)
season.after.lockdown.168.df <- data.frame(Hour=rep(1:24, 7), figure=season.after.lockdown.168$figure[c(49:168,1:48)], sd=season.after.lockdown.168$sd[c(49:168,1:48)], Weekday=rep(weekdays, each=24))
seasonbase.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
seasonbase.after.lockdown.24 <- trend_season(aggregated.after.lockdown, 24)
seasonbase.after.lockdown.24.df <- data.frame(Hour=1:24, figure=seasonbase.after.lockdown.24$figure, sd=seasonbase.after.lockdown.24$sd)
seasonbase.after.lockdown.168 <- trend_season(aggregated.after.lockdown, 168)
seasonbase.after.lockdown.168.df <- data.frame(Hour=rep(1:24, 7), figure=seasonbase.after.lockdown.168$figure[c(49:168,1:48)], sd=seasonbase.after.lockdown.168$sd[c(49:168,1:48)], Weekday=rep(weekdays, each=24))

plot_grid(
  autoplot(ts(seasonbase.after.lockdown.24.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.after.lockdown.168.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.168.df$figure + rep(season.after.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.after.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.after.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.after.lockdown.168.df$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

plot_grid(
  autoplot(ts(season.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.24$figure  - season.after.lockdown.24$sd,  ymax = season.after.lockdown.24$figure  + season.after.lockdown.24$sd),  alpha=0.5, fill = "mediumpurple1") +
    geom_line(aes(col="After lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.24$figure - season.before.lockdown.24$sd, ymax = season.before.lockdown.24$figure + season.before.lockdown.24$sd), alpha=0.5, fill = "lightcoral") +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Before lockdown")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("After lockdown", "Before lockdown")),
  autoplot(ts(season.after.lockdown.168.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.168.df$figure  - season.after.lockdown.168.df$sd,  ymax = season.after.lockdown.168.df$figure  + season.after.lockdown.168.df$sd),  alpha=0.5, fill = "mediumpurple1") +
    geom_line(aes(col="After lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.168.df$figure - season.before.lockdown.168.df$sd, ymax = season.before.lockdown.168.df$figure + season.before.lockdown.168.df$sd), alpha=0.5, fill = "lightcoral") +
    geom_line(aes(y=season.before.lockdown.168.df$figure, col="Before lockdown")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("After lockdown", "Before lockdown")),
  nrow = 2)

autoplot(ts(seasonbase.after.lockdown.168.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = (seasonbase.after.lockdown.168.df$figure - seasonbase.after.lockdown.168.df$sd), ymax = (seasonbase.after.lockdown.168.df$figure + seasonbase.after.lockdown.168.df$sd)), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="After lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168.df$figure - seasonbase.before.lockdown.168.df$sd, ymax = seasonbase.before.lockdown.168.df$figure + seasonbase.before.lockdown.168.df$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168.df$figure, col="Before lockdown")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("After lockdown", "Before lockdown"))
```
```{r seasonalities/seasonplot-mean-sd}
ggplot(data=seasonbase.before.lockdown.168.df) +
  geom_line(aes(Hour, figure - sd, col=Weekday), alpha=.1) +
  geom_line(aes(Hour, figure + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(Hour, ymin = figure - sd, ymax = figure + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(Hour, figure, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  labs(title="Seasonal plot: before lockdown") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))

ggplot(data=seasonbase.after.lockdown.168.df) +
  geom_line(aes(Hour, figure - sd, col=Weekday), alpha=.1) +
  geom_line(aes(Hour, figure + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(Hour, ymin = figure - sd, ymax = figure + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(Hour, figure, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  labs(title="Seasonal plot: after lockdown") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))
```
